Psychological Needs During Intergroup Contact

### 2022-01-05 Methods-and-Results.Rmd
robust long tbl added

```{r robustnessTbl, include=FALSE}
# Table of all robustness checks (w/ and w/out SDT only)

@@

# Wide format
mdlRobustTbl <- data.frame(
  coef = c(
    sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
    names(mdlRobustPrep[[1]]$random),
    names(mdlRobustPrep[[1]]$fit)
  )
)
for (i in 1:length(mdlRobustPrep)){
  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
}

@@

\input{Tables/mdlContactGeneral}
\input{Tables/mdlContactGeneralLong}
<!-- \input{Tables/mdlTheory} -->
\input{Tables/mdlTheorylong}
\input{Tables/mdlRobustness}

>>>>

```{r robustnessTblLong, include=FALSE}
# Table of all robustness checks (w/ and w/out SDT only)

@@

# manual assembly
shortRobustPrep <- list()
for(i in 1:length(mdlRobustPrep)){
  study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical")
  sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out")
  #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula)
  #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = ''))

  name <- paste(study, sample, sep='.')
  tmp <- rbind(
    mdlRobustPrep[[i]]$coeficients[, c("coef", "B", "Beta")],
    data.frame(
      coef = "R2Marg_R2Cond",
      B = mdlRobustPrep[[i]]$fit$R2Marg_R2Cond,
      Beta = ""
    )
  )
  shortRobustPrep[[name]] <- tmp
}

tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))]
fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef)
for (i in 1:length(tmp)){
  fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef")
}

tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))]
outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef)
for (i in 1:length(tmp)){
  outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef")
}

robustTblLong <- rbind(
  fullRobustTbl,
  outRobustTbl
)

robustTblLong$coef <- mapvalues(
  robustTblLong$coef,
  from = c(
    "R2Marg_R2Cond"
  ),
  to = c(
    "$R^2_{marginal}$ / $R^2_{conditional}$"
  )
)

mdlTblRobustLong <- robustTblLong %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Robustness Analyses",
    #format = "latex",
    linesep = "",
    booktabs = T,
    align = c("l", rep("c", ncol(.)-1)),
    escape = FALSE
  ) %>%
  kable_classic() %>%
  add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
  pack_rows("Contact [Full Sample]", 1, 5) %>%
  pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>%
  kable_styling(latex_options = "scale_down") %>%
  kableExtra::landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/mdlRobustlong.tex")
```

```{r robustnessTblWide, include=FALSE}
# Wide format
mdlRobustTbl <- data.frame(
  coef = c(
    sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
    names(mdlRobustPrep[[1]]$random),
    names(mdlRobustPrep[[1]]$fit)
  )
)
for (i in 1:length(mdlRobustPrep)){
  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
}

@@

<!-- \input{Tables/mdlContactGeneral} -->
\input{Tables/mdlContactGeneralLong}

<!-- \input{Tables/mdlTheory} -->
\input{Tables/mdlTheorylong}

\input{Tables/mdlRobustness}
\input{Tables/mdlRobustlong}
